---
title: "Assignment B1"
author: "Sabine Halabi"
date: "2022-10-31"
output: html_document
---
# Function Building
This project requires us to build a function of our choosing.

```{r}
library(tidyverse)
library(styler)
library(lintr)
library(roxygen2)
library(datateachr)
library(testthat)
```

## My Function and Documentation
To produce summary statistics for many variables in my dataset from my STAT 545A data analysis project, I had to copy-paste the same code and change the variables each time, as well as changing the dataset when I wanted to explore each dataset. I want to make it easier to run summary statistics for different datasets by creating a function that does so. Additionally, I consistently had to use the function group_by() and change the variable. This became tedious everytime I want to run group_by() %>% summarise(). 


```{r}
#' Function for Summary Statistics
#' 
#' @description Function that runs summary statistics by groups on specified variables in dataset
#' 
#' @param data dataset which includes all required variables for the function
#' @param col column name by which other variables will be grouped by
#' @param var variable for which we want to obtain summary statistics
#' @param na.rm set default as FALSE and can be specified with TRUE as needed
#' 
#' @return the function will return a tibble including the count of the variable per group of the col param, as well as columns for each summary statistics in the function per group.
#' 

summary_function <- function(data, col, var, na.rm = FALSE) {
  if(!is.numeric(data %>% pull({{var}}))){
    stop("Sorry! Variable must be numeric!")
  }
  data %>%
    group_by({{col}}) %>%
    summarise(n=n(), mean = mean({{var}}, na.rm = na.rm), median = median({{var}}, na.rm = na.rm), min = min({{var}}, na.rm = na.rm), max = max({{var}}, na.rm = na.rm), sd= sd({{var}}, na.rm = na.rm))
}
  
```

## Examples

My first example will be some datasets from datateachr:

```{r}
#summary stats for radius_mean variable in cancer dataset 
#this is an example of where a function would work

cancer_sample %>% 
  summary_function(diagnosis, radius_mean)

```
```{r}
#summary stat for flow_sample dataset
#this is an example of where the function requires na.rm = TRUE argument

flow_sample %>% 
  summary_function(extreme_type, flow, na.rm = TRUE)
```
```{r}
#summary stat for vancouver_trees dataset
# this is an example of where the function will not work because of a non-numeric argument in the var parameter

vancouver_trees %>% 
  summary_function(tree_id, genus_name)
```

```{r}
#test from gapminder dataset
#this is an example of where the function will work

gapminder %>% summary_function(continent, lifeExp)
```
```{r}
#test from gapminder dataset
#this is an example of where the function won't work because the var parameter is not numeric

gapminder %>% summary_function(continent, country)
```


## Function Test

```{r}
#there should be an error message when variable name isn't numeric
test_that("This is a test for my summary function", {
  expect_error(summary_function(vancouver_trees, tree_id, genus_name)) #Test whether an error message is given if variable is non-numeric
  expect_error(summary_function(building_permits, type_of_work, property_use)) #Another error test 
  expect_identical((summary_function(cancer_sample, diagnosis, radius_mean)),
                   (cancer_sample %>% 
                      group_by(diagnosis) %>% 
                      summarise(n=n(), mean = mean(radius_mean), median = median(radius_mean), min = min(radius_mean), max = max(radius_mean), sd = sd(radius_mean)))) #Test whether the function gives identical result as manual input
  expect_true(is_tibble(summary_function(cancer_sample, diagnosis, radius_mean))) #Test that the output is a tibble table
  }
  )
```

