---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# groupsummary

<!-- badges: start -->
<!-- badges: end -->

The **summaries** package is an R package that contains a summary function in the **R folder** that allows one to easily supply the function with a dataframe, a column by which the data should be grouped by, and a variable for which summary statistics (count, mean, median, minimum, maximum, and standard deviation) should be produced.

Follow below for installation and usage instructions.

## Installation

You can install the development version of summaries like so:

```{r}
library(devtools)

devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-halabis/groupsummary", ref = "0.1.0")
```


## Usage Examples

Below is a basic example which shows you how to conduct a common computation:

```{r cars}
library(gapminder)
library(groupsummary)

summary_function(gapminder, continent, lifeExp)

```
