---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# groupsummary

<!-- badges: start -->
<!-- badges: end -->

The **summaries** package is an R package that contains a summary function in the **R folder** that allows one to easily supply the function with a dataframe, a column by which the data should be grouped by, and a variable for which summary statistics (count, mean, median, minimum, maximum, and standard deviation) should be produced.

Follow below for installation and usage instructions.

## Installation

You can install the development version of summaries like so:

```{r}
library(devtools)

devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-halabis", subdir = '/groupsummary', ref = "0.1.0")
```


## Usage Examples

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

